Coordinated monitoring of the Piney Point wastewater discharage into Tampa Bay: Data synthesis and reporting

### 2022-05-12 manu-draft.Rmd
added synthesis and dashboard figs

* Monitoring details - effort, agencies, methods, TBEP coordination, refer to MPB paper for details
* Synthesis workflow
     * Challenges - multiple streams, messy AF
     * Solutions - centralized data uploads, R tools for synthesis (import, testing, app integration)
     * Sorta unified data structure (but see metadata section)
* Repository setup - synthesis and app

@@

* App creation and hosting
* App structure - backend
     * R/dat_proc.R to data folder, logs
     * Testing why and how (testthat, GitHub Actions)
     * Rmarkdown w/ flexdashboard: Dependencies/globals, reactives, UI setup with text descriptions and dynamic inputs
     * CSS styling
     * Google Analytics js
* App structure - frontend
     * Landing page
     * Current data
          * Water quality results
          * Algal surveys
          * Seagrass/macroalgae
          * Contaminants
          * Benthic
     * Baseline data
          * Water quality
          * Seagrasses

@@

>>>>

* Monitoring details - effort, agencies, methods, TBEP coordination, refer to MPB paper for details
* Synthesis workflow Figure \@ref(fig:synthesis)
     * Challenges - multiple streams, messy AF
     * Solutions - centralized data uploads, R tools for synthesis (import, testing, app integration)
     * Sorta unified data structure (but see metadata section)
* Repository setup - synthesis and app

@@

* App creation and hosting, Figure \@ref(fig:dashboard)
* App structure - backend
     * R/dat_proc.R to data folder, logs
     * Testing why and how (testthat, GitHub Actions)
     * Rmarkdown w/ flexdashboard: Dependencies/globals, reactives, UI setup with text descriptions and dynamic inputs
     * CSS styling
     * Google Analytics js
* App structure - frontend
     * Landing page
     * Current data
          * Water quality results
          * Algal surveys
          * Seagrass/macroalgae
          * Contaminants
          * Benthic
     * Baseline data
          * Water quality
          * Seagrasses

@@

```{r synthesis, fig.cap = 'Data synthesis workflow for Piney Point data.  Raw data were uploaded by partners to Google Drive, data were synthesized using R-based tools, data and dashboard code were uploaded in a unified format on GitHub that included automated testing, and then the app was deployed using Shiny Server.'}
knitr::include_graphics(here('figs/synthesis.JPG'))
```

```{r dashboard, fig.cap = 'Landing page for the Piney Point dashboard. Users can view a summary of effort to date and access additional tabs to view specific datasets.'}
knitr::include_graphics('figs/dashboard.JPG')
```
